A Taxonomy of Twists of Supersymmetric Yang--Mills Theory

### 2020-01-31 paper.tex
merge

\begin{abstract}
We give a complete classification of twists of supersymmetric Yang-Mills theories with in dimensions~$2\leq n \leq 10$.
We formulate supersymmetric Yang-Mills theory classically using the BV formalism, and then we construct an action by the supersymmetry algebra using the language of $L_\infty$ algebras.
For each class of square-zero supercharges in the supersymmetry algebra, we give a description of the corresponding twisted theory in terms of partially holomorphic and topological versions of Chern-Simons and $BF$ theory. 
\end{abstract}

@@

\subsection*{Applications to quantization and a relationship to factorization algebras}
\addcontentsline{toc}{subsection}{Applications to quantization and a relationship to factorization algebras}

The quantization of gauge theories is notoriously subtle and leads to a rich theory of renormalization.
An attractive application of the descriptions of the twists of supersymmetric gauge theories that we provide is to study quantization.

To rigorously study the quantization of supersymmetric Yang-Mills theory we can work with the mathematical theory of renormalization developed by Costello in \cite{CosRenorm}. 
In the context of (non-supersymmetric) Yang-Mills theory it is shown that this theory of re

@@

Observe that the quadruple of fields $\{\chi^*, \chi, \wt\chi^*, \wt\chi\}$ has the same Poisson brackets as the quadruple $\{\chi^*-t\wt\chi^*, \chi, \wt\chi^*, \wt\chi + t\chi\}$. Therefore, we may eliminate the fields $\chi^*-t\wt\chi^*, \chi$ using Proposition \ref{prop:integrateoutfield}. We then have trivial BRST doublets $\{\wt\chi + t\chi, \wt a\}$, $\{\nu, \wt \nu\}$ and $\{\rho, A_{1, 0}\}$ which may be eliminated using Proposition \ref{prop:BRSTdoublet}. We are left with the action
\[S_{BF} + t \int\dvol\left(-(b, A_{0, 1}^*) + a c^* + \frac{1}{2} \xi^* B^* + t (\varphi, \phi^*) + \frac 14 (\psi^*, \psi^*) \right),\]
where $S_{BF}$ is the action functional of the holomorphic twist at $t=0$ found in the previous section. 
Since the extra terms are quadratic in the fields, the claim is reduced to a comparison of the underlying local $L_\infty$ algebra of the twisted theory and that of the holomorphic Hodge theory. The former is given by (cf. the proof of Theorem \ref{thm:4dholomorphictwist})
\[
\xymatrix@R=0.5cm@C=0cm{
\ul{-1} & \ul{0} & \ul{1} & \ul{2} & \ul{3} & \ul{4} \\ 
& \Omega^0(\CC^2; \gg)_c \ar[r] &\Omega^{0,1}(\CC^2; \gg)_{A_{0,1}} \ar[r] &\Omega^{0,2}(\CC^2; \gg)_{B} \\
\Omega^0(\CC^2; \gg)_a  \ar@{-->}^{t\id}[ur] \ar[r] &\Omega^{0,1}(\CC^2; \gg)_{b}  \ar@{-->}^{t\id}[ur] \ar[r] &\Omega^{0,2}(\CC^2; \gg)_{\xi^*}  \ar@{-->}^{t\id}[ur] \\
& &  \Omega^{2,0}(\CC^2 ; \gg)_{B^*}  \ar@{-->}^{t\id}[dr] \ar[r] & \Omega^{2,1}(\CC^2 ; \gg)_{A_{0,1}^*} \ar[r]  \ar@{-->}^{t\id}[dr] & \Omega^{2,2}(\CC^2 ; \gg)_{c^*}  \ar@{-->}^{t\id}[dr] \\
& & & \Omega^{2,0}(\CC^2; \gg)_\xi \ar[r] &\Omega^{2,1}(\CC^2; \gg)_{b^*} \ar[r] &\Omega^{2,2}(\CC^2; \gg)_{a^*}  \\
& & \Omega^0(\CC^2 ; U\otimes K^{1/2})_\phi \ar[r] & \Omega^{0,1}(\CC^2 ; U\otimes K^{1/2})_\psi \ar[r] & \Omega^{0,2}(\CC^2 ; U\otimes K^{1/2})_{\varphi^*} \\
& \Omega^{2,0}(\CC^2 ; U\otimes K^{-1/2})_{\varphi} \ar[r]  \ar@{-->}^{t\id}[ur] & \Omega^{2,1}(\CC^2 ; U\otimes K^{-1/2})_{\psi^*} \ar[r]  \ar@{-->}^{t\id}[ur]  & \Omega^{2,2}(\CC^2 ; U\otimes K^{-1/2})_{\phi^*}  \ar@{-->}^{t\id}[ur]
}
\]
which is exactly the local $L_\infty$ algebra of the holomorphic Hodge theory.
\end{proof}

@@

\chris{I just made the following attempt}
\begin{theorem}
The twist of 4d $\cN=4$ super Yang--Mills with respect to the family $Q_t$ of square-zero supercharges of Equation \ref{eq:4d412Hodgefamily} is perturbatively equivalent to $\map\left(\CC_{\rm Dol} \times \RR^2_{\mr{dR}}, B\fg_{\Hod}\right)$. Moreover, this equivalence is $\spin(2;\RR) \times \spin(2;\RR)$-equivariant.
\end{theorem}

\begin{proof}
Fix a rank $(2,1)$ supercharge of the form $Q_{st} = Q_0 + tQ_1 + sQ_2$, where $Q_t = Q_0 + tQ_1$ is a rank $(2,0)$ supercharge lying within a 4d $\mc N=2$ subalgebra of the 4d $\mc N=4$ supertranslation algebra.  Consider the supersymmetry actions 
\begin{align*}
&I^{(1)}(Q_0 + tQ_1 + sQ_2) \\
&I^{(2)}(Q_0 + tQ_1 + sQ_2, Q_0 + tQ_1 + sQ_2).
\end{align*}
We will compute the corresponding $\ZZ$-graded $Q_{st}$-twisted theory.  Let us first recall the steps of the proof of Theorem \ref{thm:4dDonaldsontwist}: the twist of 4d $\mc N=2$ super Yang-Mills with matter by $Q_t$.  We will do the same thing to eliminate fields in the $Q_{st}$-twisted theory.  The key fact is that the part of the deformation of the action proportional to $s$, namely
\[I^{(1)}(sQ_2) + 2 I^{(2)}(Q_0, sQ_2) + 2 I^{(2)}(tQ_1, sQ_2) + I^{(2)}(sQ_2, sQ_2)\]
only includes terms involving both $\mc N=4$ fields in the set $\{c, A_{1,0}, A_{0,1}, a, \wt a, \chi \wt \chi, b, B, \xi, \rho\}$ coming from the $\mc N=2$ vector multiplet (plus their antifields) \emph{and} $\mc N=4$ fields in the set $\{\nu, \wt \nu, \phi, \psi, \varphi\}$ coming from the $\mc N=2$ hypermultiplet (and their antifields).  More precisely, the action involves the images of the fields in these sets after restricting from $\mr U(2)$-representations to $\spin(2;\RR) \times \spin(2;\RR)$-representations.  In what follows we will write $\mr U(2)$-expressions, with the understanding that the further deformation by $sQ_2$ will further break these component fields.

So, we first performed a chance of variables sending $\{\chi^*, \chi, \wt\chi^*, \wt\chi\}$ to $\{\chi^*-t\wt\chi^*, \chi, \wt\chi^*, \wt\chi + t\chi\}$: this only used the fact that the two quadruples had the same Poisson brackets, which still applies here.  We then used Proposition \ref{prop:integrateoutfield} to eliminate the fields $\chi^*-t\wt\chi^*, \chi$.  The proposition still applies here, because the further twist by $sQ_2$ does not introduce a $\chi^2$ or $(\chi^*-t\wt\chi^*)^2$ term.  Finally, we used Proposition \ref{prop:BRSTdoublet} to eliminate the trivial BRST doublets $\{\wt\chi + t\chi, \wt a\}$, $\{\nu, \wt \nu\}$ and $\{\rho, A_{1, 0}\}$.  Again, the proposition still applies here: each time we apply the proposition, we must only ensure that there are no terms in the twisted action proportional to a pair of fields $(X, Y)$, we need only observe that the deformation could not introduce terms to the action proportional to $XX^*$ or $YY^*$.

As a result of this argument, we are free -- as in the proof of Theorem \ref{thm:4dDonaldsontwist}, to set the eliminated fields $\chi, \wt \chi, \wt a, \nu, \wt \nu, \rho$ and $A_{1,0}$ to 0 in the twisted action functional.  This twisted action coincides with the sum of the $Q_0 + sQ_2$-twisted action functional from Theorem \ref{thm:4d_11_twist}, with the deformation by $tQ_1$, namely
\[\left(I^{(1)}(tQ_1) + 2 I^{(2)}(Q_0, tQ_1) + I^{(2)}(tQ_1, tQ_1)\right) + 2I^{(2)}(tQ_1, sQ_2).\]
The deformation given by the first three terms was computed in the proof of Theorem \ref{thm:4dDonaldsontwist} to be
\begin{equation}
\label{eq:4d_12_further_deformation}
t \int\dvol\left(-(b, A_{0, 1}^*) + a c^* + \frac{1}{2} \xi^* B^* + t (\varphi, \phi^*) + \frac 14 (\psi^*, \psi^*) \right).
\end{equation}
The fourth and final term, proportional to $st$, vanishes after the field elimination we have performed, since $\Gamma_{10}(Q_1,Q_2) = 0$, and the remaining term from equation \ref{eq:gaugeI2}, of form $st(Q_1,\lambda^*)(Q_2,\lambda^*)$, is proportional to $(Q_1,\lambda^*)$, which is proportional to $\chi^*$.

Therefore, the $Q_{st}$ twisted action theory is equivalent to the rank $(1,1)$-twisted theory from Theorem \ref{thm:4d_11_twist}, with action deformed by the expression \ref{eq:4d_12_further_deformation}.  This deformation gives the desired theory.  The rank $(1,1)$-twisted theory was $\ZZ$-graded, and the deformation here by $tQ_1$ is a deformation by a degree 1 operator, so the twisted theory is also $\ZZ$-graded.  Finally, the rank $(1,1)$-twisted theory was shown to be $\spin(2;\RR) \times \spin(2;\RR)$-invariant, and the deformation \ref{eq:4d_12_further_deformation} was $\MU(2)$-equivariant, so the rank $(1,2)$-twisted theory is still $\spin(2;\RR) \times \spin(2;\RR)$-invariant.

\subsubsection{Rank \texorpdfstring{$(2, 2)$}{(2,2)} twist}
\label{sect:4dqgltwist}

>>>>

\begin{abstract}
We give a complete classification of supersymmetric twists of super Yang-Mills theories with matter in all dimensions.  Super Yang-Mills theories can be modelled classically using the BV formalism; we construct the supersymmetry algebra action using the language of $L_\infty$ algebras, then for each class of square-zero supercharge we give a description of the corresponding twisted theory in terms of partially holomorphic versions of Chern-Simons and BF theory. 
\end{abstract}

@@

@@

Observe that the quadruple of fields $\{\chi^*, \chi, \wt\chi^*, \wt\chi\}$ has the same Poisson brackets as the quadruple $\{\chi^*-t\wt\chi^*, \chi, \wt\chi^*, \wt\chi + t\chi\}$. Therefore, we may eliminate the fields $\chi^*-t\wt\chi^*, \chi$ using Proposition \ref{prop:integrateoutfield}. We then have trivial BRST doublets $\{\wt\chi + t\chi, \wt a\}$ and $\{\rho, A_{1, 0}\}$ which may be eliminated using Proposition \ref{prop:BRSTdoublet}. We are left with the action
\[S_{BF} + t \int\dvol\left(-(b, A_{0, 1}^*) + a c^* + \frac{1}{2} \xi^* B^* + t (\varphi, \phi^*) + \frac 14 (\psi^*, \psi^*) \right),\]
where $S_{BF}$ is the action functional of the holomorphic twist at $t=0$ found in the previous section. 
Since the extra terms are quadratic in the fields, the claim is reduced to a comparison of the underlying local $L_\infty$ algebra of the twisted theory and that of the holomorphic Hodge theory. The former is given by (cf. the proof of Theorem \ref{thm:4dholomorphictwist})
\[
\xymatrix@R=0.5cm@C=0cm{
\ul{-1} & \ul{0} & \ul{1} & \ul{2} & \ul{3} & \ul{4} \\ 
& \Omega^0(\CC^2; \gg)_c \ar[r] &\Omega^{0,1}(\CC^2; \gg)_{A_{0,1}} \ar[r] &\Omega^{0,2}(\CC^2; \gg)_{B} \\
\Omega^0(\CC^2; \gg)_a  \ar@{-->}^{t\id}[ur] \ar[r] &\Omega^{0,1}(\CC^2; \gg)_{b}  \ar@{-->}^{t\id}[ur] \ar[r] &\Omega^{0,2}(\CC^2; \gg)_{\xi^*}  \ar@{-->}^{t\id}[ur] \\
& &  \Omega^{2,0}(\CC^2 ; \gg)_{B^*}  \ar@{-->}^{t\id}[dr] \ar[r] & \Omega^{2,1}(\CC^2 ; \gg)_{A_{0,1}^*} \ar[r]  \ar@{-->}^{t\id}[dr] & \Omega^{2,2}(\CC^2 ; \gg)_{c^*}  \ar@{-->}^{t\id}[dr] \\
& & & \Omega^{2,0}(\CC^2; \gg)_\xi \ar[r] &\Omega^{2,1}(\CC^2; \gg)_{b^*} \ar[r] &\Omega^{2,2}(\CC^2; \gg)_{a^*}  \\
& & \Omega^0(\CC^2 ; U\otimes K^{1/2})_\phi \ar[r] & \Omega^{0,1}(\CC^2 ; U\otimes K^{1/2})_\psi \ar[r] & \Omega^{0,2}(\CC^2 ; U\otimes K^{1/2})_{\varphi^*} \\
& \Omega^{2,0}(\CC^2 ; U\otimes K^{-1/2})_{\varphi} \ar[r]  \ar@{-->}^{t\id}[ur] & \Omega^{2,1}(\CC^2 ; U\otimes K^{-1/2})_{\psi^*} \ar[r]  \ar@{-->}^{t\id}[ur]  & \Omega^{2,2}(\CC^2 ; U\otimes K^{-1/2})_{\phi^*}  \ar@{-->}^{t\id}[ur]
}
\]
which is exactly the local $L_\infty$ algebra of the holomorphic Hodge theory.
\end{proof}

@@

\end{proof}
\subsubsection{Rank \texorpdfstring{$(2, 2)$}{(2,2)} twist}
\label{sect:4dqgltwist}
